\textls[-0]{\thetitle}

### 2023-03-24 metatheory2.tex
reply

%Since we work in an intrinsic-typed setting, some required premises can be omitted without ambiguity. For omitted context judgement $\goodCtx{\Gm}{k}$, the universe level is always $k$, hinted at the figure of judgement specification. Similar for type judgement $\goodType{\Gm}{T}{j}$.
\EDJ{Why removing the mentioning of ``omitted/inferrable k here?'' I know it is confusing but I think it is important to make things rigorous.}\YZreply{I agree it's important, and I'm happy to include it if you make it less confusing.}\EDJreply{Do you think ``omitting premises'' should be mentioned here or earlier?}

>>>>

%Since we work in an intrinsic-typed setting, some required premises can be omitted without ambiguity. For omitted context judgement $\goodCtx{\Gm}{k}$, the universe level is always $k$, hinted at the figure of judgement specification. Similar for type judgement $\goodType{\Gm}{T}{j}$.
\EDJ{Why removing the mentioning of ``omitted/inferrable k here?'' I know it is confusing but I think it is important to make things rigorous.}\YZreply{I agree it's important, and I'm happy to include it if you make it less confusing.}\EDJreply{Do you think ``omitting premises'' should be mentioned here or earlier?}\YZreply{It's not just about omitting premises, right? You also omit universal levels in some typing rules.}
